---
title: "Beer Vs Wings"
author: "Andrew Martin-Smith"
date: "11/30/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.align = "center", message = FALSE)
library(ggplot2)
```




## Beer Vs Wings

```{r}
beerwings <- read.csv("http://www1.appstate.edu/~arnholta/Data/Beerwings.csv")
DT::datatable(beerwings[, 2:4])
```


## Graph

```{r, echo = FALSE}
ggplot(data = beerwings, aes(x = Beer, y = Hotwings)) +
  geom_point(aes(color = Gender)) + 
  labs(x = "Beer", y = "Hotwings") + 
  theme_bw() + 
  scale_color_manual(values = c("hotpink", "darkblue"))
```
This graph shows the amount of wings to consumed compared the amount in fluid ounces were consumed in a sitting with differentiation of sex.

## Where to get Beer and Wings in Boone

The Ale house has good wing deals on Thursday nights for 35 cents a wing, but also Monday through Thursday from 11pm - 2am has deals on various meals including wings. They also have various different drink and beer specials throughout the week.

The Rock has 55 cent wings and $1.50 Keystone cans on Monday nights.

Tapp Room you can get wings at menu price and various different beer specials from $2 - $4 throughout the week.

## What I Used

```{r, echo = TRUE, eval = FALSE}
ggplot(data = beerwings, aes(x = Beer, y = Hotwings)) +
  geom_point(aes(color = Gender)) + 
  labs(x = "Beer", y = "Hotwings") + 
  theme_bw() + 
  scale_color_manual(values = c("hotpink", "darkblue"))
```

This is the code that I used to make the graph and is essentially putting together what I have learned from this class With using R.

## THE END



